---
title: "Final Project"
format: html
editor: visual
---

## Final Project Table

```{r}
#| label: tbl-one
#| tbl-cap: "Covid results"
table1 <- Descriptive_Table

knitr::kable(table1)
```

```{r}
#| label: regression
#| tbl-cap: "Covid results"
figure1 <- tbl_uvregression(
	covid_testing,
	y = age,
	include = c(col_rec_tat, rec_ver_tat),
	label = list(
		col_rec_tat ~ "Time elapsed, collect time to receive time",
		rec_ver_tat ~ "Time elapsed,  receive time to verification time"
	),
	method = lm)
knitr::kable(figure1)
```

```{r}
#| label: fig-one
hist(covid_testing$age)
```

```{r}
pos_age <- inline_text(table1, variable = "age", 
                         column = "positive")
neg_age <- inline_text(table1, variable = "age", 
                         column = "negative")
```

@tbl-one contains a table of demographics by Covid test result, including age, gender, and patient class.

@fig-one contains a histogram of Covid-testing by patient age.

The average age of patients with positive Covid tests (`r pos_age`) was greater than the average age of patients with negative Covid tests (`r neg_age`) patients tested positive for Covid-19.

```{r}
stats <- list(n = nrow(table1),
              mean_age = mean(table1$age))
```

There were `r stats$n` total participants with a mean age of `r stats$mean_age`.
