---
title: "Final Project"
format: html
editor: visual
---

## Final Project Table
```{r}
install.packages("medicaldata")
library(medicaldata)

data(package = "medicaldata")

covid <- medicaldata::covid_testing

install.packages("gtsummary")
library(gtsummary)

table1 <- tbl_summary(
covid,
	by = result,
	include = c(age, gender, patient_class),
	label = list(
		age ~ "Patient Age",
		gender ~ "Patient Gender",
		patient_class ~ "Patient Class"
	),
	missing_text = "Missing") |>
	add_p(test = list(all_continuous() ~ "t.test",
										all_categorical() ~ "chisq.test")) |>
	add_overall(col_label = "**Total**") |>
	bold_labels() |>
	modify_footnote(update = everything() ~ NA) |>
	modify_header(label = "**Variable**", p.value = "**P**")
```

```{r}
#| label: tbl-one
#| tbl-cap: "Covid results"

knitr::kable(table1)
```

```{r}
#| label: regression
#| tbl-cap: "**Covid results**"
figure1 <- tbl_uvregression(
	covid_testing,
	y = age,
	include = c(col_rec_tat, rec_ver_tat),
	label = list(
		col_rec_tat ~ "Time elapsed, collect time to receive time",
		rec_ver_tat ~ "Time elapsed,  receive time to verification time"
	),
	method = lm)
knitr::kable(figure1)
```

```{r}
#| label: fig-one
#| fig-cap: "**Covid Testing by Age**"

hist(covid_testing$age)
```

```{r}
pos_age <- inline_text(table1, variable = "age", 
                         column = "positive")
neg_age <- inline_text(table1, variable = "age", 
                         column = "negative")
```

@tbl-one contains a table of demographics by Covid test result, including age, gender, and patient class.

@fig-one contains a histogram of Covid-testing by patient age.

The average (range) age of patients with positive Covid tests (`r pos_age`) was greater than the average (range) age of patients with negative Covid tests (`r neg_age`) patients tested positive for Covid-19.

```{r}
stats <- list(n = nrow(covid),
              mean_age = round(mean(covid$age), digits = 2))
```

There were `r stats$n` total participants with a mean age of `r stats$mean_age`.
